---
title       : Predict stopping distance for cars
subtitle    : 
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Purpose

This app will help predict how long it takes for a car to stop depending on fast it's traveling.   

## Data

The data used for this app is from the cars dataset from the R datasets packages. The data give the speed of cars and the distances taken to stop. The format of the dataset is data frame with 50 observations on 2 variables.

1. Speed (mph)
2. Stopping distance (ft) 

---

## Analysis

We are going to use a simple linear regression model for our calculation.
``` {r}
require(ggplot2)
g = ggplot(cars, aes(x = speed, y = dist))
g = g + xlab("Speed (mph)")
g = g + ylab("Stopping distance (ft)")

```

---

```{r}
g = g + geom_point(size = 7, colour = "black", alpha=0.5)
g = g + geom_point(size = 5, colour = "blue", alpha=0.2)
g = g + geom_smooth(method = "lm", colour = "black")
g
```

---

```{r}
model <- lm(dist ~ speed, cars)
model$coeff
```


## Predict

Now we are going to use the coefficients out of the model to predict using the very basic formula:
y = y_intercept + speed * x. Please use the app in order to predict what the stopping distance would be given the speed of the car.